The eclipse of ASASSN-21qj

### 2022-09-19 src/tex/ms.tex
[showyourwork] overleaf sync

@@

   \begin{enumerate}
      \item There was a collision between planetoids towards ASASSN-21qj which generated a debris cloud.
      \item The cloud moved in front of the star, and we have a fresh measure of the debris from a collision.
   \end{enumerate}

>>>>

\textcolor{magenta}{Probing disintegrating planetary material has been proven to be a very useful method to access the composition of building blocks of planets outside of the Solar System. E.g. the disintegration of a gas giant around a white dwarf was used to infer its composition \citep{Gaensike2019}. White dwarf star pollution has also yielded insights about refractory (Fe/Mg/Ca) element content of rocky  material around such stars \citep{Turner2020,Putirka2021,Blouin2020}. See also \cite{Veras2021} for a review.}

\textcolor{magenta}{Planets and asteroids falling into white dwarfs, however, haven been probably heavily processed during the late stellar evolution. The unusually warm (how much?) debris disk passing in front of a young star presented in this work, on the other hand, may allow to probe the interior of planetisimals in the early stages of planet formation. The eclipse is expected to last for xxx days, allowing to perform further spectroscopic analysis of the dust in this system.}

@@

   \begin{enumerate}
      \item There was a collision between planetoids towards ASASSN-21qj which generated a debris cloud.
      \item The cloud moved in front of the star, and we have a fresh measure of the debris from a collision.
     \item \textcolor{magenta}{Probing dust of material in the early stages of planet formation is complementary to studies of white dwarf polluters. The latter represent planetary material after the end of the main sequence of the host star. }
   \end{enumerate}
